---
title: "Seminor6"
author: "OyieyoSilas"
date: "2023-05-18"
output: html_document
---
#Looking at different options for model programming.
#main package for simulations is decisionSupport.
#Installing the package and recall it in the library.
```{r}

library(decisionSupport)
#plot the impact pathway
#simple pathway transformed into codes using mermaid function

library(DiagrammeR)
#impact pathway diagram
mermaid("graph LR
        Y(Yield)-->I(Income); linkStyle 0 stroke:green, stroke-width:1px
        M(Market price)-->I; linkStyle 1 stroke: green, stroke-width:1px
        I-->F(Final result); linkStyle 2 stroke: green, stroke-width:1.5px
        CL(Labor cost)-->F; linkStyle 3 stroke: red, stroke-width:1.5px")

mermaid("graph LR
        w(biomass)-->r(rootdev); linkStyle 0 stroke: red, stroke-width: 1.4px
        T(roottype)-->r; linkStyle 1 stroke: green, stroke-width:1.5px ")

mermaid("graph TD
        Y(Yield)-->I(Income); linkStyle 0 stroke:green, stroke-width:1px
        M(Market price)-->I; linkStyle 1 stroke: green, stroke-width:1px
        I-->F(Final result); linkStyle 2 stroke: green, stroke-width:1px
        CL(Labor cost)-->F; linkStyle 3 stroke: red, stroke-width:1px
        CM(Management cost)-->F; linkStyle 4 stroke: red, stroke-width:1px")

```


#Model building

```{r cars}
#Model building
input_estimated <- data.frame(variable = c("Yield", "Market_price", "Labour_cost", "Management_cost"),
                              lower = c(6000, 3, 500, 100),
                              median = NA,
                              upper = c(14000, 8, 1000, 2000),
                              distribution = c("posnorm", "posnorm", "posnorm", "posnorm"),
                              label = c("Yield (kg/ha)", "Price (USD/kg)", "Labor cost (USD/ha)", "mgt cost(USD/ha)"),
                              Description = c("Yield in a sweet cherry farm under normal conditions",
                                              "Price of sweet cherry in a normal season",
                                              "Labor costs in a normal season",
                                              "Management costs in a normal season"))
input_estimated


```

# Model function
## i didnt understand the function bracket. what to feed in. i encountered some errors

```{r}
library(decisionSupport)
                                  #didnot understood what to be in (function())below
model_function <- function(input_estimated){
# Estimate the income in a normal season
income <- Yield * Market_price


#summarize management and labour cost into overall cost
overall_cost <- (Labour_cost + Management_cost)


# Estimate the final results from the model
final_result <- income - overall_cost

# Generate the list of outputs from the Monte Carlo simulation
return(list(final_result = final_result))}

# Run the Monte Carlo simulation using the model function
example_mc_simulation <- mcSimulation(estimate = as.estimate(input_estimated),
                                      model_function = model_function,
                                      numberOfModelRuns = 800,
                                      functionSyntax = "plainNames")

#example_mc_simulation
```

#Generatuing the plots.
#ploting the histogram
#setting method argument to histogram function. ploting will visualize the Monte Carlo simulation results.

```{r}
library(ggplot2)
plot_distributions(mcSimulation_object = example_mc_simulation,
                   vars = "final_result",
                   method = "hist_simple_overlay",
                   old_names = "final_result",
                   new_names = "Outcome distribution for profits")

```
#rather running full model
#testing with ,make_variables. make_variables and as.estimate to the data with default n=1 generate random data
#note. each time the code is run it generate new values of data.
```{r}
make_variables <- function(est, n=1)
{ x<-random(rho=est, n=n)
for(i in colnames(x)) assign(i, as.numeric(x[1, i]), envir=.GlobalEnv)
}

#with the data i generated(example_mc_simulation)
make_variables(as.estimate(input_estimated))
Labour_cost+Management_cost


# generating random values for variables of "input_estimates
#make_variables(as.estimate(input_estimates))
#Market_price #output: 5.895449
#Labor_cost #output: 643.7335
#Management_cost #output: 836.1038
#Labor_cost+Management_cost #output: 1479.8373
  
```




